An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 Revision/response.tex

\begin{figure*}[t]  % 或者 [b] 放到底部
	\centering
%	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
	\caption{Effect of Attribute Distribution on Query Performance}
	\label{fig:attribute_distribution}
\end{figure*}

For performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure. This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates. As shown in Figure~\ref{fig:attribute_selectivity} below.

%We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}. We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.

@@

	% 第二行：两张子图，左侧宽度是右侧的两倍
	\begin{subfigure}{0.627\textwidth} % 2/3 宽度
		\centering

		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_2.pdf}
		\caption{Algorithms Optimized for High AS}
		\label{fig:exp_5_2_2}
	\end{subfigure}
	\hspace{1mm} % 增加水平间距
	\begin{subfigure}{0.33\textwidth} % 1/3 宽度
		\centering

		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_3.pdf}
		\caption{Algorithms Insensitive to AS}
		\label{fig:exp_5_2_3}
	\end{subfigure}

	\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
	\label{fig:attribute_selectivity}
\end{figure*}
%\begin{figure}[htbp]
%	\centering
%	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
%	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
%	\caption{Different AS under the Same Algorithm}
%	\label{fig:attribute_selectivity_2}
%\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Some figures (e.g., performance under different attribute distributions or selectivity) are dense and could benefit from cleaner presentation or summarization to improve readability.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your feedback. We have modified both the figure and the related description in the paper to improve readability. For more  details, please refer to our response to Meta R1.

%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{It would strengthen the paper to delve into multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We have added complex multi-modal query experiments and provided an in-depth analysis of the results. For more details, please refer to our response to Meta R2.
%We think this is an excellent suggestion. We have enhanced our experiments by incorporating more complex multimodal dataset evaluations in Section \textcolor{blue}{XXX} of the paper. Initially, our paper utilized the Text2Image dataset, which is commonly used in existing multimodal ANN algorithms. This dataset presents a modality gap, as the base vectors are images while the query set consists of text, often requiring algorithms to exhibit stronger robustness for good performance. To further enrich the evaluation of complex multimodal queries, we selected 500,000 text vectors and 500,000 image vectors from the Text2Image dataset to form a mixed base query dataset. Similarly, we chose 5,000 image vectors and 5,000 text vectors as query vectors, combining both text and image modalities. We then performed attribute filtering and range queries on this multimodal dataset to further analyze algorithm robustness.  The relevant experimental results are presented and discussed in Section\textcolor{blue}{XXX}of our paper.

### 2025-07-31 VLDB2026/main.tex
1

		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

\textcolor{blue}{
In addition,our experiments show that different algorithms exhibit varying strengths under different query ranges. Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value. For example, UNIFY demonstrates strong generality by dynamically selecting execution strategies based on the query range. Building on this idea, further exploration of more adaptive and high-performance range query algorithms is a promising direction for future research.}

Moreover, in our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.

>>>>

		\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

%	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search. To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes. UNIFY newly proposes segment graphs and integrates multiple data structures to process queries. Although UNIFY performs slightly worse on small-range queries, its proposed index structure broadens the research direction.

\textcolor{blue}{
Experimental results show that different algorithms exhibit varying strengths under different query ranges. Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value. For example, UNIFY demonstrates strong generality by dynamically selecting execution strategies based on the query range. Building on this idea, further exploration of more adaptive and high-performance range query algorithms is a promising direction for future research.}

In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.
